%!TEX ROOT=sample-thesis.tex
%!TEX PROGRAM=xelatex

\chapter{Conclusions and Future Works}

This chapter presents the conclusions and the identified future works of this thesis. This chapter firstly describes how the aim and objectives of this study are fulfilled. Next, the contributions of this thesis and the significance of the work carried out in this study are highlighted. Lastly, this chapter describes the limitations of this study and suggests possible future works.
\\ \\ \indent
The remainder of this chapter is as follows. In Section 5.1, the accomplishment of the aim and objectives of this study are described. Section 5.2 then highlights the contributions of this thesis. Section 5.3 presents the significance of this work. Finally, the limitations and future works are discussed in Section 5.4.

\section{Aim and Objectives Achievement}
This study aimed to enable visual analysis for facilitating instructors in MOOC learner support monitoring using visual analytics. This section explains how the research aim was attained by accomplishing the following objectives.

\subsection{Investigate the recent visual analytics designs and applications to identify current design gap}
This study accomplished this objective by reviewing the most credible published visualization studies via scholarly databases. Recent visualization literature published in the most prominent visualization journals and conferences were visited and thoroughly examined. This study then analyzed and classified the recent visual analytics designs and applications and identify four design challenges: visual usability, scalability, interactivity, information appertains.

