%!TEX ROOT=sample-thesis.tex
%!TEX PROGRAM=xelatex

\noindent
Massive open online course (MOOCs) is now the prevalent form of online courses with the rise of online learning platforms like Coursera and EdX. Online learning platforms do provide pre-set analytics that enable instructors to explore their data. However, pre-set visual analytics usability is restricted by preconfigured analysis mode and display when involving large MOOC data. Literature indicates that available MOOC visualization design dominantly focuses on enabling visual analysis for MOOC analysts, with limited attention on dominant target user which is the instructors. Furthermore, limited visualization designs were found that consider user roles and focuses on enabling instructor’s frequent course monitoring. This limitation is further investigated and a gap in design knowledge was found concerning visualization for learner support monitoring. This study aims to enable visual analysis on MOOC learner support monitoring for instructors using problem-driven approaches. The usability design gap was identified by systematically examining the visualization design space of visual analytics for MOOC. Analysis tasks, design requirements, data dimensions, and visualization techniques reported in visualization literature were examined and discussed. To address the gap, this study proposed a user-centered visual analytics design MOOCSupport that enables instructors to perform visual analysis on learner support monitoring. Five domain experts were interviewed to derive problem characterization and abstraction and identify design requirements. MOOCSupport was methodically designed with systematic consideration on its visualization features for great usability and learnability. Case study and interviews with six domain experts have demonstrated the usefulness and effectiveness of MOOCSupport in facilitating instructor’s visual analysis. Visualization designers can leverage MOOCSupport and the presented design experience to support MOOC instructors in learner support monitoring.
 
